% Created 2021-11-10 Wed 08:44
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Reid Chen, Gaoyi Hu}
\date{\today}
\title{P4}
\hypersetup{
 pdfauthor={Reid Chen, Gaoyi Hu},
 pdftitle={P4},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.5)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents



\section{\texttt{Symb}}
\label{sec:org95908c0}
This class is used to store variables. The \texttt{kind} field is used to indicate the kind of declaration:
\begin{itemize}
\item \texttt{struct}
\item \texttt{func}
\item \texttt{var}
\end{itemize}
\section{\texttt{FnSymb}}
\label{sec:org7634e91}
This class is used to store functions. The \texttt{formals} field is used to store the function's parameters. The \texttt{toString} method reveals the type of this function.
\section{\texttt{StructSymb}}
\label{sec:orgc3f72ff}
This class is used to store the definitions of \texttt{struct}. It stores the fields that the \texttt{struct}. The \texttt{containsField} method can be used to check if an \texttt{id} is of this struct or not.
\section{\texttt{ASTnode}}
\label{sec:orgd754bb8}
\begin{itemize}
\item A various of static methods have been declared in this class for displaying the \texttt{ErrMsg}.
\item A \texttt{analyze} method has been added to each subclass of \texttt{ASTnode}. The symbol table \texttt{table} is passed along the ast to achieve the name analysis.
\end{itemize}
\section{\texttt{ErrMsg}}
\label{sec:orgbe0bccc}
The field \texttt{TRIGGERED} is set to true if and only if the \texttt{fatal} method has been called. This \texttt{TRIGGERED} is checked in \texttt{P4} after name analyzing phase to decide if \texttt{unparse} should be called or not.
\end{document}
